%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Dakota Murray - vita},
	pdfauthor={Dakota Murray},
	pdfproducer={http://dakotamurray.me}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

% DOCUMENT
\begin{document}
{\LARGE Dakota S. Murray}\\[0.5cm]
Phone: \texttt{+1 (828) 691 5724}\\
email: \href{mailto:dakmurra@iu.edu}{dakmurra@iu.edu}; \href{mailto:dakota.s.murray@gmail.com}{dakota.s.murray@gmail.com}\\
\textsc{url}: \href{http://www.dakotamurray.me}{http://www.dakotamurray.me}\\ 
\textsc{Orcid id:}  \href{http://orcid.org/0000-0002-7119-0169}{0000-0002-7119-0169}\\
\textsc{github:}  \href{https://github.com/murrayds}{https://github.com/murrayds}


\section*{Current Position}
Research Assistant\\
School of Informatics, Computing, and Engineering, Indiana University Bloomington

\section*{Areas of Specialization}
Science of Science  • Computational Social Science • Data Science
 
%%\hrule
\section*{Education}
\noindent
\years{2016-present}\textsc{Ph.D.} in Informatics\\
Track in \textit{Computing, Culture, and Society}; Minor in \textit{Statistics}\\
School of Informatics, Computing, and Engineering, Indiana University Bloomington\\
\textit{advisors:} Dr. Cassidy R. Sugimoto and Dr. Yong-Yeol Ahn\\
\\
\years{2012-2016}\textsc{B.S.} in Computer Science\\
Department of Computer Science, Appalachian State University\\
\textit{advisor:} Dr. Mitch Parry

\section*{Appointments and Employment}
\noindent
\years{2019-present}Research Assistant\\
Dr. Yong-Yeol Ahn, \textit{Science Genome Project}\\
School of Informatics, Computing, and Engineering, Indiana University\\
\\
\years{2018-2019} Associate Instructor\\ 
School of Informatics, Computing, and Engineering, Indiana University\\
\\
\years{2017 (Summer)} Visiting Scholar\\
Center for Science and Technology Studies, Leiden University\\
\\
\years{2016-2018}Research Assistant\\
Dr. Cassidy Sugimoto, \textit{Scholarly Communication Lab}\\
School of Informatics, Computing, and Engineering, Indiana University\\
\\
\years{2013-2016}Research Assistant and Web Developer\\
Department of Computer Science, Appalachian State University\\
\\
\newpage
\years{2015 \\(Summer \& Fall)}NIFS Student Intern\\
NASA Langley Research Center\\

\section*{Publications}

\subsection*{Journal articles and Indexed Conference Proceedings}

\years{2019} \hangindent=0.7cm \textbf{Murray, D.}, Boothby, C., Zhao, H., Minik, V., Bérubé, N., Larivière, V., \& Sugimoto, C. R. (2019). Exploring the personal and professional factors associated with student evaluations of teachers. SocArXiv. \\

\years{2019} \hangindent=0.7cm Robinson-Garcia, N., Sugimoto, C. R., \textbf{Murray, D.}, Yegros-Yegros, A., Larivière, V., \& Costas, R. (2019). The many faces of mobility: Using bibliometric data to measure the movement of scientists. Journal of Informetrics, 13(1), 50–63. \\

\years{2019} \hangindent=0.7cm Bu, Y., \textbf{Murray, D. S.}, Xu, J., Ding, Y., Ai, P., Shen, J., \& Yang, F. (2018). Analyzing scientific collaboration with “giants” based on the milestones of career. Proceedings of the Association for Information Science and Technology, 55(1), 29–38. \\

\years{2018} \hangindent=0.7cm \textbf{Murray, D.}, Siler, K., Lariviére, V., Collings, A. M., Raymond, J., Sugimoto, R., (under revision). Gender and international diversity improves equity in peer review. PLOS Bio. \\

\years{2018} \hangindent=0.7cm Robinson-Garcia, N., Sugimoto, C. R., \textbf{Murray, D.}, Yegros-Yegros, A., Larivière, V., \& Costas, R. (2018). Scientific mobility indicators in practice: International mobility profiles at the country level. El Profesional de La Información, 27(3), 511. \\

\years{2018} \hangindent=0.7cm Bu, Y., Ding, Y., Liang, X., \& \textbf{Murray, D. S. }(2018). Understanding persistent scientific collaboration. Journal of the Association for Information Science and Technology, 69(3), 438–448. \\

\years{2018} \hangindent=0.7cm Bu, Y., \textbf{Murray, D. S.}, Ding, Y., Huang, Y., \& Zhao, Y. (2018). Measuring the stability of scientific collaboration. Scientometrics, 114(2), 463–479. \\

\years{2018} \hangindent=0.7cm Chinchilla-Rodríguez, Z., Miao, L., \textbf{Murray, D.}, Robinson-García, N., Costas, R., \& Sugimoto, C. R. (2018). A Global Comparison of Scientific Mobility and Collaboration According to National Scientific Capacities. Frontiers in Research Metrics and Analytics, 3. \\

\years{2017} \hangindent=0.7cm Sugimoto, C. R., Robinson-Garcia, N., \textbf{Murray, D. S.}, Yegros-Yegros, A., Costas, R., \& Larivière, V. (2017). Scientists have most impact when they’re free to move. Nature, 550(7674), 29–31. \\

\years{2017} \hangindent=0.7cm Das, S., Goard, J., \& \textbf{Murray, D.} (2017), How Celebrities Feed Tweeples with Personal and Promotional Tweets: Celebrity Twitter Use and Audience Engagement. In Proceedings of the 8th International Conference on Social Media and Society (pp. 30:1–30:5). New York, NY, USA: ACM. 

\subsection*{Other publications}
\noindent

\years{2019} \hangindent=0.7cm Sugimoto C, Allen L, Jeroen B et al. Rethinking Impact Factors: New Pathways in Journal Metrics. F1000Research 2019, 8:671 (document). 

\years{2018} \hangindent=0.7cm Cassidy R. Sugimoto, \textbf{Dakota S. Murray}, and Vincent Larivière (April 26, 2018), "Open citations to open science", \emph{ISSI Blog}. 

\years{2017} \hangindent=0.7cm Rodrigo Costas, Alfredo Yegros, Vincent Larivière, Cassidy Sugimoto, Nicolas Robinson-Garcia, \textbf{Dakota S. Murray} (October 5, 2017), "The global scientific brain: Policy implications of barriers to scientific mobility", \emph{CWTS Blog}. 

\section*{Conference Works and Talks}

\subsection*{Refereed conference works}

\years{2019} \hangindent=0.7cm \textbf{Murray, D}., Larivière, V., Sugimoto C. R., (2019). Context matters: how the usage and semantics of hedging terms differs between sections of scientific papers. ISSI2019. Rome, Italy.\\

\years{2019} \hangindent=0.7cm  \textbf{Murray, D}., Lamers, W., Boyack K., Larivière, V., Sugimoto C. R., van Eck, N., Waltman L., (2019). Measuring disagreement in science. ISSI2019. Rome, Italy.\\

\years{2019} \hangindent=0.7cm Miao, L., \textbf{Murray, D}., Larivière, V., Sugimoto, C., Jung, W-S., \&  Yeol, Y-Y., (2019). The disciplinary structure of nation's scientific production. NetSci2019. Burlington, Vermont, USA.\\

\years{2017} \hangindent=0.7cm \textbf{Murray, D.}, Zhou, H., Minik, V., Larivière, V., \& Sugimoto, C. R., (2017). Are Great Researchers Terrible Teachers? How research and teaching performance relate at U.S. universities. ISSI2017. Wuhan, China\\

\years{2017} \hangindent=0.7cm Robinson-Garcia, N., Sugimoto, C.R., \textbf{Murray, D.}, Yegros-Yegros, A., Lariviere, V., \& Costas, R. (2017). Unveiling the multiple faces of mobility: Towards a taxonomy of scientific mobility types based on bibliometric data. STI2017. Paris, France.\\

\years{2017} \hangindent=0.7cm Chinchilla-Rodriguez, Z., Miao, L., \textbf{Murray, D.}, Robinson-Garcia, N., Costas, R., \& Sugimoto, C.R. (2017). A large-scale comparison of the position of countries in international collaboration and mobility according to their scientific capacities. STI2017. Paris, France.\\

\years{2017} \hangindent=0.7cm \textbf{Murray, D.}, Sugimoto, C.R., \& Lariviere, V. (2017). A balanced portfolio? The relationship between gender and funding for US academic professors. STI2017. Paris, France.\\

\years{2017} \hangindent=0.7cm Miao, L., \textbf{Murray, D.}, Chinchilla-Rodriguez, Z., Lariviere, V., \& Sugimoto, C.R. (2017). Glass boundaries: Differences in interdisciplinarity between men and women. STI2017. Paris, France.

\subsection*{Panels}
\years{2018} \hangindent=0.7cm Zaida Chinchilla-Rodríguez, presented by \textbf{Dakota Murray }, (2018) Moving on up: the relationship between international mobility and global leadership. 4S, Sydney, Australia\\

\years{2018} \hangindent=0.7cm Cassidy Sugimoto, \textbf{Dakota Murray}, \&  Vincent Larivière, Open panel,\emph{The Global Scientific Brain: International Mobility of the Scientific Workforce}, 4S Sydney, Sydney, Australia

\subsection*{Workshops and Schools}
\years{2019} \textit{Complex Networks Winter Workshop}, Quebec City, Canada\\
\years{2019}Invited Scholar, \textit{MIDAS Data Science Symposium}, Ann Arbor, Michigan\\
\years{2019} Santa Fe Institute's \textit{Summer School in Complex Systems}, Santa Fe, New Mexico\\
\years{2017} Lorentz Center Workshop \emph{Rethinking Impact Factors: New Pathways in Journal Metrics}, Leiden, Netherlands.\\

%\hrule
\section*{Grants, honors, and awards}
\subsection*{Grants and other funding}
\years{2019} GISA Departmental Travel Award, School of Informatics, Computing, and Engineering - \$950 \\
\years{2017-2018} Integrated Doctoral Education with Application to Scholarly Communication (IDEASc) fellowship, Institute of Museum and Library Services\\
\years{2017} Cross-track collaboration travel grant, School of Informatics, Computing, and Engineering - \$500\\

\subsection*{Academic awards}
\years{2016}Graduated B.S. \emph{Summa Cum Laude} and with departmental honors\\
\years{2012-2016} Chancellor's List (GPA > 3.85), Appalachian State Univeristy\\
\years{2012, 2013} NSF Academy of Science Scholarship at Appalachian State University

\section*{Teaching}

\subsection*{Indiana University Bloomington}
\years{Fall 2018-Spring 2019}Associate Instructor, Informatics Capstone I \& II: Design and Development of an Information System

\subsection*{Appalachian State University}
\years{2015-2016}Computer Science Tutor, Appalachian State University\\
\years{2013}Lab Assistant, Computer Science I and II

\subsection*{Guest Lectures}
\years{Fall 2019}Excel workshop for beginners, \textit{Understanding Social Data} at IU\\
\years{Fall 2019}Introduction to Machine Learning, Sociology 110, \textit{Understanding Social Data}\\
\years{Fall 2019}A gentle overview of academic conferences in Informatics 501:  \textit{Introduction to Informatics}\\
\years{Spring 2018}Invited presenter and discussion leader in Informatics 501: \emph{Introduction to Informatics}.

%\hrule
\section*{Service}

\subsection*{Reviewing}
(Year of first review): \emph{International Journal of Information Management} (2019);  \emph{Scientometrics} (2019); \emph{PLoS Computational Biology} (2019); \emph{PLoS One}
 (2017); \emph{Journal of Informetrics} (2017); \emph{Journal of the Association for Information Science \& Technology} (2017)

\subsection*{Indiana University Bloomington}
\years{2017-2018}Representative, Graduate and Professional Student Government, Indiana University Bloomington\\
\years{2017}Publicity Chair, Graduate Informatics Student Association, Indiana University Bloomington\\
\years{2016}Social Chair, Graduate Informatics Student Association, Indiana University Bloomington

\subsection*{Professional organizations}
\years{2018 - present} Member, Society for the Social Studies of Science\\
\years{2017 - present}Member, International Society for Scientometrics and Informetrics

\vspace{1cm}
\vfill{}
\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
%\fontspec{Times New Roman}
\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
\href{http://nitens.org/taraborelli/cvtex}{http://nitens.org/taraborelli/cvtex}}
\end{center}

\end{document}